Visualising Life Satisfaction in Countries across Europe: Individual- and Multi-Level Evidence on Cultural and Pecuniary Factors

### 2019-01-31 LaTex/Paper_fulltext.tex
Geo data description

\section{Data}
All data employed in this project is acquired from official sources and with permission of the provider or in the course of open access. Data as well as original codebooks will be made available for the user upon request, or delivered within the project.
The project is mainly built on data from the 'European Value Study 2008' (EVS), which is the fourth survey wave \citep{evs_european_2016}. The EVS contains questions regarding values of Europeans on aspects like moral, work, family, politics, society, religion, as well as an extensive collection of socio-demographic items. Issues and questions regarding surveying of the data, errata, harmonizing of results etc. may be settled with the publisher or from the original codebook. The file contains a total 66281 observations for 477 variables over 46 European countries. All transformations on variables can be read in detail from the codebook. Significant changes to the data were made through exclusion of 'Russian Federation' from the sample for the purpose of better visualisation. Furthermore, 'Northern Cyprus' and 'Northern Ireland' which were coded as own countries were added to their respective states after international law. Thus, data for 43 countries was processed for use in the project. Furthermore, aggregations were made from the data in total of 5 cases to create variables that are applicable for multilevel analysis. Finally, a variable of 'Geographical region' was created from the country variable in the EVS. This classification was based on the 'Standard Country or Area Codes for Statistics Use' from the UN Statistics Division \citep{unsd_standard_2019}.
Structural data for nations was obtained from the World Bank for 'GDP per capita of 2008' (in 2018 dollars per inhabitant)\citep{world_bank_gdp_2019}, and for 'Gini Coefficient 2008' (in ration scale 0-1)\citep{world_bank_gini_2019}. In the case of 'Gini Coefficient 2008', missing values for Germany, Poland, Serbia, Kosovo, Macedonia, Croatia and Bosnia Herzegovina were taken from Eurostat 2008 (Germany, Poland) \citep{eurostat_eurostat_2019}, from the CIA World Factbook (Serbia 2008) \citep{central_intelligence_agency_serbia_2019}, from World Bank Gini Coefficient 2009 (Kosovo, Macedonia, Croatia), and from World Bank Gini Coefficient 2007 (Bosnia Herzegovina) \citep{world_bank_gini_2019}. Data was also obtained from the 'Democracy Cross-National' dataset created by Pippa Norris \citep{norris_data_2015} for the Freedom House Democracy rating 2008 and the Human Development Index 2008. Missing values of the Freedom House rating for Kosovo \citep{freedom_house_kosovo_2012} and Montenegro \citep{freedom_house_montenegro_2012} were replaced by the indication for 2008 on the Freedom House website. The missing value of the HDI 2008 for Kosovo was approximated by the value for Serbia in 2008.

@@

\begin{tabular}{|c|c|c|}
	\hline 
	\textbf{Project area}	& \textbf{Noah Peters} 	& \textbf{Nicolas Goeller} 	\\ 
	\hline 
	Data wrangling			&  		   				&  				 			\\ 
	\hline 
	Variable preparation 	&  		   				&  				 			\\ 
	\hline 
	Geodata					&  		   X			&  				 			\\ 
	\hline 
	Git	     			 	&  		   				&  				X 			\\ 
	\hline 			
	Indices				 	&  		   X			&  				 			\\ 
	\hline 
	Paper visualisations 	&  		   				&  				 			\\ 
	\hline 
	Shiny 				 	&  		   				&  				X 			\\ 
	\hline 
	Codebook 			 	&  		   				&  				X 			\\ 
	\hline 
	Geoplots 			 	&  		   X			&  				 			\\ 
	\hline 
	LaTex				 	&  		   				&  				 			\\ 
	\hline 
	Motivation			 	&  		   				&  				X 			\\ 
	\hline 
	Theory				 	&  		   X			&  				 			\\ 
	\hline 
	User manual			 	&  		   				&  				 			\\ 
	\hline 
\end{tabular}

@@

	\hangindent=\parindent
	\parindent 0pt
	\hangafter=-1
	All indirect or direct sources are acknowledged in the bibliography. We are aware that a false declaration is punishable by law. 
	\\
	\\
	\\
	Place, date                                         	Signature Noah Peters
	\\
	\\
	\\
	\\
	\\
	Place, date												Signature Nicolas Goeller

>>>>

\section{Data}
All data employed in this project is acquired from official sources and with permission of the provider or in the course of open access. Data as well as original codebooks will be made available for the user upon request, or delivered within the project.
The project is mainly built on data from the 'European Value Study 2008' (EVS), which is the fourth survey wave \citep{evs_european_2016}. The EVS contains questions regarding values of Europeans on aspects like moral, work, family, politics, society, religion, as well as an extensive collection of socio-demographic items. Issues and questions regarding surveying of the data, errata, harmonizing of results etc. may be settled with the publisher or from the original codebook. The file contains a total 66281 observations for 477 variables over 46 European countries. All transformations on variables can be read in detail from the codebook. Significant changes to the data were made through exclusion of 'Russian Federation' from the sample for the purpose of better visualisation. Furthermore, 'Northern Cyprus' and 'Northern Ireland' which were coded as own countries were added to their respective states after international law. Thus, data for 43 countries was processed for use in the project. Furthermore, aggregations were made from the data in total of 5 cases to create variables that are applicable for multilevel analysis. Finally, a variable of 'Geographical region' was created from the country variable in the EVS. This classification was based on the 'Standard Country or Area Codes for Statistics Use' from the UN Statistics Division \citep{unsd_standard_2019}.
Structural data for nations was obtained from the World Bank for 'GDP per capita of 2008' (in 2018 dollars per inhabitant)\citep{world_bank_gdp_2019}, and for 'Gini Coefficient 2008' (in ration scale 0-1)\citep{world_bank_gini_2019}. In the case of 'Gini Coefficient 2008', missing values for Germany, Poland, Serbia, Kosovo, Macedonia, Croatia and Bosnia Herzegovina were taken from Eurostat 2008 (Germany, Poland) \citep{eurostat_eurostat_2019}, from the CIA World Factbook (Serbia 2008) \citep{central_intelligence_agency_serbia_2019}, from World Bank Gini Coefficient 2009 (Kosovo, Macedonia, Croatia), and from World Bank Gini Coefficient 2007 (Bosnia Herzegovina) \citep{world_bank_gini_2019}. Data was also obtained from the 'Democracy Cross-National' dataset created by Pippa Norris \citep{norris_data_2015} for the Freedom House Democracy rating 2008 and the Human Development Index 2008. Missing values of the Freedom House rating for Kosovo \citep{freedom_house_kosovo_2012} and Montenegro \citep{freedom_house_montenegro_2012} were replaced by the indication for 2008 on the Freedom House website. The missing value of the HDI 2008 for Kosovo was approximated by the value for Serbia in 2008. \\
To obtain national geo data for European countries, the `rnaturalearth' package was used \citep{south_rnaturalearth:_2017}.
Geo data for European regions (NUTS1 2006) were obtained from Eurostat with the according package \citep{lahti_eurostat:_2019}. For the 
processing of geo data, the `sf' package was employed \citep{pebesma_sf:_2018}.

@@

\begin{tabular}{|c|c|c|}
	\hline 
	\textbf{Project area}	& \textbf{Noah Peters} 	& \textbf{Nicolas Goeller} 	\\ 
	\hline 
	Data wrangling			&  		   X			&  				X 			\\ 
	\hline 
	Variable preparation 	&  		   X			&  				X 			\\ 
	\hline 
	Geodata					&  		   X			&  				 			\\ 
	\hline 
	Git	     			 	&  		   				&  				X 			\\ 
	\hline 			
	Indices				 	&  		   X			&  				 			\\ 
	\hline 
	Paper visualisations 	&  		   				&  				X 			\\ 
	\hline 
	Shiny 				 	&  		   				&  				X 			\\ 
	\hline 
	Codebook 			 	&  		   				&  				X 			\\ 
	\hline 
	Geoplots 			 	&  		   X			&  				 			\\ 
	\hline 
	LaTex				 	&  		   X			&  				 			\\ 
	\hline 
	Motivation			 	&  		   				&  				X 			\\ 
	\hline 
	Theory				 	&  		   X			&  				 			\\ 
	\hline 
	User manual			 	&  		   				&  				X 			\\ 
	\hline 
\end{tabular}

@@

	\hangindent=\parindent
	\parindent 0pt
	\hangafter=-1
	All indirect or direct sources are acknowledged in the bibliography. We are aware that a false declaration is punishable by law. 
	\\
	\\
	\\
	Place, date                                         	Signature Noah Peters
	\\
	Copenhagen, January 31th 2019\\
	\\
	\\
	\\
	Place, date												Signature Nicolas Goeller
	\\
	Lehrensteinsfeld, January 31th 2019
